Implementing Real-time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
Adds TCP Hollywood architecture diagram, and accompanying text

>>>>

The architecture of TCP Hollywood \cite{mcquistin2016hollywood} is shown in
Figure \ref{diagram:tcp-hollywood}. TCP Hollywood provides all of the
services described in Section \ref{sec:services}, with functionality split
across an intermediary layer (in userspace), and a set of modifications to
the kernel. The intermediary layer is responsible for providing the
message-oriented abstraction, and exposing the API for partial reliability.
The kernel modifications implement the deadline and dependency services,
as well as enabling out-of-order delivery of incoming segments. This split
allows applications to use a single API, whether or not the kernel
modifications are available. TCP Hollywood inherits standard TCP's
congestion control mechanism. Clearly, this loss-based mechanism is not
suitable for real-time applications, and a delay-based algorithm should
be adopted.

\begin{figure}[t]
 \centering
 \includegraphics[scale=0.965]{figures/tcp-hollywood.pdf}
 \caption{TCP Hollywood architecture}
\label{diagram:tcp-hollywood}
\end{figure}
